Learning with Misspecified Models: The Case of Overestimation\\ \href{https://jimena-galindo.github.io/fileRepo/draft.pdf}{\normalsize Click Here for the Latest Version}

### 2023-11-09 Paper/draft.Rmd
Added references to paper

@Ba2023 moves away from dogmatism and endows the agents with a mechanism through which they can abandon incorrect beliefs. This allows them to avoid falling into learning traps. To do so, agents perform Bayesian hypothesis tests that evaluate which of two possible parameters is more likely. By doing so, she characterizes the set of situations in which even agents who consider alternative paradigms may become trapped.\footnote{A similar mechanism is proposed by \citet{Schwarstein2021} in a setting with persuasion.}

@@

@@

The overall pattern is that bad news are associated with a decrease in effort, and a more negative news differential is associated with a larger decrease in effort. On the contrary, good news are associated with a small decrease in effort. As mentioned in the predictions section, this is consistent with the self-attribution bias as well as with a change of paradigm. It is not consistent with the dogmatic modeler or the Bayesian. In addition, the fact that about a third of the subjects started with a correctly specified belief and ended up overconfident is consistent only with the self-attribution bias. This points towards the fact that misattribution bias is the most likely explanation for the aggregate behavior of the subjects in the experiment.

@@

These two differences present as consistent with the self-attribution bias, however, the pattern in the
stereotype treatment could also be due to self-censoring of the subjects. In particular, subjects who
initially underestimated the performance of the other participant might have realized their mistake and
over-compensated their mistake by overestimating it after good news. This is consistent with the data
and offers a more intuitive explanation for why this pattern arises in the stereotype treatment.

>>>>

@Ba2023 moves away from dogmatism and endows the agents with a mechanism through which they can abandon incorrect beliefs. This allows them to avoid falling into learning traps. To do so, agents perform Bayesian hypothesis tests that evaluate which of two possible parameters is more likely. By doing so, she characterizes the set of situations in which even agents who consider alternative paradigms may become trapped.\footnote{A similar mechanism is proposed by \citet{Schwarstein2021} in a setting with persuasion.} A more general model in this spirit is also illustrated by @Ortoleva2012, where the agent has a prior over priors and acts according to the most likely belief.

@@

A more general model that can be considered here is that of @Ortoleva2012. In his model agents have a prior over priors and choose a single prior to act according to. If this prior over priors only considers degenerate beliefs, the model will essentially reduce to the setting described here. The main difference is that in order to determine if there is a paradigm shift, the agent does not compare the likelihoods of two models, he simply looks at the likelihood of the current model and decides to switch paradigms if the likelihood is below a certain threshold. In this model the agent thus considers all possible theories and has a more flexible rule for that allows for paradigm shifts.

@@

The overall pattern is that bad news are associated with a decrease in effort, and a more negative news differential is associated with a larger decrease in effort. On the contrary, good news are associated with a small decrease in effort.\footnote{This asymmetric treatment of good and bad news has also been recently documented by \citet{Coutts2019} and @Barron2021} As mentioned in the predictions section, this is consistent with the self-attribution bias as well as with a change of paradigm. It is not consistent with the dogmatic modeler or the Bayesian. In addition, the fact that about a third of the subjects started with a correctly specified belief and ended up overconfident is consistent only with the self-attribution bias. This points towards the fact that misattribution bias is the most likely explanation for the aggregate behavior of the subjects in the experiment.

@@

These two differences present as consistent with the self-attribution bias, however, the pattern in the
stereotype treatment could also be due to self-censoring of the subjects. In particular, subjects who
initially underestimated the performance of the other participant might have realized their mistake and
over-compensated their mistake by overestimating it after good news. This is consistent with the data
and offers a more intuitive explanation for why this pattern arises in the stereotype treatment. It is also consistent with the findings of @Bohren2019, where they find that subjects initially underestimate the ability of women, however, after a sequence of good news for a woman, the attitude reverts and subjects evaluate that particlar woman to be better than men.

### 2023-11-09 Paper/draft.tex
Added references to paper

\title{Learning with Misspecified Models: The Case of Overestimation\\
\href{https://jimena-galindo.github.io/fileRepo/draft.pdf}{\normalsize Click Here for the Latest Version}}
\author{Jimena Galindo}
\date{October 26, 2023}

@@

\citet{Ba2023} moves away from dogmatism and endows the agents with a
mechanism through which they can abandon incorrect beliefs. This allows
them to avoid falling into learning traps. To do so, agents perform
Bayesian hypothesis tests that evaluate which of two possible parameters
is more likely. By doing so, she characterizes the set of situations in
which even agents who consider alternative paradigms may become
trapped.\footnote{A similar mechanism is proposed by \citet{Schwarstein2021} in a setting with persuasion.}

@@

@@

These two differences present as consistent with the self-attribution
bias, however, the pattern in the stereotype treatment could also be due
to self-censoring of the subjects. In particular, subjects who initially
underestimated the performance of the other participant might have
realized their mistake and over-compensated their mistake by
overestimating it after good news. This is consistent with the data and
offers a more intuitive explanation for why this pattern arises in the
stereotype treatment.

>>>>

\title{Learning with Misspecified Models: The Case of Overestimation\\
\href{https://jimena-galindo.github.io/fileRepo/draft.pdf}{\normalsize Click Here for the Latest Version}}
\author{Jimena Galindo}
\date{November 08, 2023}

@@

\citet{Ba2023} moves away from dogmatism and endows the agents with a
mechanism through which they can abandon incorrect beliefs. This allows
them to avoid falling into learning traps. To do so, agents perform
Bayesian hypothesis tests that evaluate which of two possible parameters
is more likely. By doing so, she characterizes the set of situations in
which even agents who consider alternative paradigms may become
trapped.\footnote{A similar mechanism is proposed by \citet{Schwarstein2021} in a setting with persuasion.}
A more general model in this spirit is also illustrated by
\citet{Ortoleva2012}, where the agent has a prior over priors and acts
according to the most likely belief.

@@

A more general model that can be considered here is that of
\citet{Ortoleva2012}. In his model agents have a prior over priors and
choose a single prior to act according to. If this prior over priors
only considers degenerate beliefs, the model will essentially reduce to
the setting described here. The main difference is that in order to
determine if there is a paradigm shift, the agent does not compare the
likelihoods of two models, he simply looks at the likelihood of the
current model and decides to switch paradigms if the likelihood is below
a certain threshold. In this model the agent thus considers all possible
theories and has a more flexible rule for that allows for paradigm
shifts.

@@

These two differences present as consistent with the self-attribution
bias, however, the pattern in the stereotype treatment could also be due
to self-censoring of the subjects. In particular, subjects who initially
underestimated the performance of the other participant might have
realized their mistake and over-compensated their mistake by
overestimating it after good news. This is consistent with the data and
offers a more intuitive explanation for why this pattern arises in the
stereotype treatment. It is also consistent with the findings of
\citet{Bohren2019}, where they find that subjects initially
underestimate the ability of women, however, after a sequence of good
news for a woman, the attitude reverts and subjects evaluate that
particlar woman to be better than men.
